R Notebook

### 2016-10-31 manuscript/draft.Rmd

Quality of predictions is important:
  * helps determine policy/set priorities
  * something something climate change
  * need to know both accuracy of point estimates and how reasonable our prediction intervals are.
  * Overconfident predictions can be worse than uncertainty
  * Quality of prediction is one metric for how much we know about ecological processes
Unclear how much to trust existing predictions:
  * Strong assumptions (see "misc" below)
  * many *interesting* predictions
  * Potential problems with confidence intervals
  * Potential disconnect between training target and actual goals
  * Difficult to test model assumptions/predictions because of time scales
    * Most scientists making predictions today will have retired by 2050
Demonstrate best practices \& their contribution to better predictions
  * Use long-term data sets such as BBS to evaluate predictive skill
  * Note the large change in average temperatures since the 80's; comparable to the changes expected in the next N years
  * Lots of talk about how we should do it, fewer examples of doing them all together
  * Examples of best practices
    * Not just bioclim
    * Dynamic predictor variables (not just site-level averages over 50 years like 
      Worldclim)
    * time series models (temporal autocorrelation)
    * spatial/site-level stuff (repeated measures aren't fully independent)
    * Properly handling uncertainty:
      * probabilistic/error bars
      * error propagation
    * multiple models
      * Test with simple baselines (e.g. random walk, future-is-like-present)
  * Focus on richness/diversity because \[citations saying that it's important\]
  * Publish forecasts at different timescales to evaluate performance/credibility
Here we do that:
  * forecasts for biodiversity in NAmerican birds with as many best practices as possible
  * Discuss the influence of these improved methods \& of our error rates on our ability to understand:
    * How to improve
    * How much to trust the predictions

>>>>

Quality of predictions is important:
  * helps determine policy/set priorities
  * something something climate change
  * need to know both accuracy of point estimates and how reasonable our prediction intervals are.
  * Overconfident predictions can be worse than uncertainty
  * Quality of prediction is one metric for how much we know about ecological processes
Unclear how much to trust existing predictions:
  * Strong assumptions (see "misc" below)
  * many *interesting* predictions
  * Potential problems with confidence intervals
  * Potential disconnect between training target and actual goals
  * Difficult to test model assumptions/predictions because of time scales
    * Most scientists making predictions today will have retired by 2050
Demonstrate best practices \& their contribution to better predictions
  * Use long-term data sets such as BBS to evaluate predictive skill
  * Note the large change in average temperatures since the 80's; comparable to the potential changed in the next 20 years 
  * Lots of talk about how we should do it, fewer examples of doing them all together
  * Examples of best practices
    * Not just bioclim
    * Dynamic predictor variables (not just site-level averages over 50 years like 
      Worldclim)
    * time series models (temporal autocorrelation)
    * spatial/site-level stuff (repeated measures aren't fully independent)
    * Properly handling uncertainty:
      * probabilistic/error bars
      * error propagation
    * multiple models
      * Test with simple baselines (e.g. random walk, future-is-like-present)
  * Focus on richness/diversity because \[citations saying that it's important\]
  * Publish forecasts at different timescales to evaluate performance/credibility
Here we do that:
  * forecasts for biodiversity in NAmerican birds with as many best practices as possible
  * Discuss the influence of these improved methods \& of our error rates on our ability to understand:
    * How to improve
    * How much to trust the predictions
